Poker Chips, Earthquakes, and Computation

### 2014-10-12 finaldraft.tex
More changes to Computation

In order to keep our notation compact we once again define a function that outputs the neighbors of a node
\begin{definition} 
Let $n(i,j)d$ be the set of neighbors of node $(i,j)$ 
\begin{equation*}
n(i,j) = \{ (x_1, y_1); (x_1 = i+1 \text{ or } x_1=i-1), \text{ and }(x_1, y_1) \in G_d\}
\end{equation*}
\end{definition}

@@

\begin{lemma}
Let $A(i)$ be the set of active nodes in an execution of board $b$ with input node $i$. Then $A(0) \subset A(1)$.
\end{lemma}

\begin{proof}
By Theorem~\ref{thm:order}, we can simulate an execution of the board with input be 0 before we apply earthquakes to the input node. We start with a board $b$ where the input is 1, so it has 4 chips. We simulate by applying earthquakes to the active nodes that are not the input. If the input node ever receives more than $8$ chips, we apply one earthquake to the input node. This way, we guarantee that the input node always contains more than $4$ chips. In addition, the input node does not contain more than $7$ chips for more than one consecutive earthquake.
We do this until every node except the input node has less than 4 chips.

Note that this execution is indistinguishable from the execution with input set to 0. This means that all nodes activated in the execution with input 0 are the same as the nodes activated in the above mentioned execution.

Once this is done, then we continue with the execution applying the earthquake to the input node. By Theorem~\ref{thm:order}, the final configuration will be the same as any execution of the board. So $A(0) \subset A(1)$.
\end{proof}

>>>>

In order to keep our notation compact we once again define a function that outputs the neighbors of a node
\begin{definition} 
Let $n(i,j)d$ be the set of neighbors of node $(i,j)$.
\end{definition}

@@

%\begin{lemma}
%Let $A(i)$ be the set of active nodes in an execution of board $b$ with input node $i$. Then $A(0) \subset A(1)$.
%\end{lemma}

%\begin{proof}
%By Theorem~\ref{thm:order}, we can simulate an execution of the board with input be 0 before we apply earthquakes to the input node. We start with a board $b$ where the input is 1, so it has 4 chips. We simulate by applying earthquakes to the active nodes that are not the input. If the input node ever receives more than $8$ chips, we apply one earthquake to the input node. This way, we guarantee that the input node always contains more than $4$ chips. In addition, the input node does not contain more than $7$ chips for more than one consecutive earthquake.
%We do this until every node except the input node has less than 4 chips.

%Note that this execution is indistinguishable from the execution with input set to 0. This means that all nodes activated in the execution with input 0 are the same as the nodes activated in the above mentioned execution.

%Once this is done, then we continue with the execution applying the earthquake to the input node. By Theorem~\ref{thm:order}, the final configuration will be the same as any execution of the board. So $A(0) \subset A(1)$.
%\end{proof}
